### 2019-09-17 README.Rmd
update README, remove param_vals

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/mlr-org/mlr3spatiotemporal.svg?branch=master)](https://travis-ci.org/mlr-org/mlr3spatiotemporal)
[![CRAN\_Status\_Badge](http://www.r-pkg.org/badges/version-ago/mlr3spatiotemporal)](https://cran.r-project.org/package=mlr3spatiotemporal)
[![cran checks](https://cranchecks.info/badges/worst/mlr3spatiotemporal)](https://cran.r-project.org/web/checks/check_results_mlr3spatiotemporal.html)
[![CRAN Downloads](https://cranlogs.r-pkg.org/badges/mlr3spatiotemporal)](https://cran.rstudio.com/web/packages/mlr3spatiotemporal/index.html)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Coverage status](https://codecov.io/gh/mlr-org/mlr3spatiotemporal/branch/master/graph/badge.svg)](https://codecov.io/github/mlr-org/mlr3spatiotemporal?branch=master)
<!-- badges: end -->

@@

task = tsk("ecuador")
resampling = rsmp("spcv-coords")
resampling$param_set$values = list(folds = 5)
resampling$instantiate(task)

>>>>

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/mlr-org/mlr3spatiotemporal.svg?branch=master)](https://travis-ci.org/mlr-org/mlr3spatiotemporal)
[![CRAN Status Badge](https://www.r-pkg.org/badges/version-ago/mlr3spatiotemporal)](https://cran.r-project.org/package=mlr3spatiotemporal)
[![cran checks](https://cranchecks.info/badges/worst/mlr3spatiotemporal)](https://cran.r-project.org/web/checks/check_results_mlr3spatiotemporal.html)
[![CRAN Downloads](https://cranlogs.r-pkg.org/badges/mlr3spatiotemporal)](https://cran.rstudio.com/web/packages/mlr3spatiotemporal/index.html)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Coverage status](https://codecov.io/gh/mlr-org/mlr3spatiotemporal/branch/master/graph/badge.svg)](https://codecov.io/github/mlr-org/mlr3spatiotemporal?branch=master)
<!-- badges: end -->

@@

task = tsk("ecuador")
resampling = rsmp("spcv-coords", folds = 5)
resampling$instantiate(task)
